# General Trend

```{r Imports, include=FALSE,echo=FALSE}
library(tidyverse)
library(RCurl)
library(plyr)
library(dplyr)
library(forcats)
library(parcoords)
library(scales)
library(mosaic)
library(vcd)
```

```{r files, include=FALSE,echo=FALSE}
AggregateData <- read.csv(file = '/Users/tracy/Desktop/columbia/vis/final_table.csv',header = TRUE)
AggregateData$`FISCAL.YEAR` <- as.ordered(AggregateData$`FISCAL.YEAR`)
AggregateData <- AggregateData %>% dplyr::rename( "year" = "FISCAL.YEAR")
yearly_proposal <- distinct(select(AggregateData, TITLE, year))
yearly_home <- distinct(select(AggregateData, `PERSONNEL.DEPARTMENT.NAME`, year))
yearly_primary <- distinct(select(AggregateData, `PRIMARY.RESPONSIBLE.DEPARTMENT.NAME`, year))

mytheme <- theme(axis.text=element_text(size = 10),
  axis.title=element_text(size=14, face = "bold"),
  plot.title = element_text(size = 14.5, face = "bold",hjust = 0.5),
  legend.title = element_text(size = 14),
  legend.text = element_text(size = 12))
```

**Connections between Personnel Home Department and Primary Responsible Department**

In order to have a general look at the participated departments and primary responsible departments, I draw an interactive node network to show all related departments. In the plot, the blue nodes shows the primary departments. 
**Note:** Only the first several letters of the department name is shown on the node, if you move your mouse on the nodes, you will see the full names.

  <head>
    <title>Organization Graph Diagram</title>
    <style>
    <link rel="stylesheet" href="styles.css">
      body {
        margin: 0;
        overflow: hidden;
        font-family: sans-serif;
      }
    </style>
    <script src="https://unpkg.com/d3@6.2.0/dist/d3.min.js"></script>
  </head>
  <body>
    <svg id="container" width="960" height="1220"></svg>
    <script src="scripts/nodes.js"></script>
  </body>

As we can see from the plot, DSI has participated in many proposals that are related to various departments at Columbia University. However, this interactive network shows all the departments that appeared after 2013. To see the variations of proposal numbers, personnel home department numbers and primary responsible department numbers over years, I use bar charts to illustrate the variations.


```{r proposal_nums, fig.width=8, fig.height=3.5,fig.align = "center"}
#yearly_proposal
ggplot(yearly_proposal, aes(year))+
  geom_bar(color ="grey50", fill ="lightblue") +
  xlab("year")+
  ylab("counts")+
  ggtitle("Number of Proposals via years")+
  mytheme
```
```{r home_dept_nums, fig.width=8, fig.height=3.5,fig.align = "center"}
#yearly_home_dept
ggplot(yearly_home, aes(year))+
  geom_bar(color ="grey50", fill ="lightblue") +
  xlab("year")+
  ylab("counts")+
  ggtitle("Number of Participated Home Depts via years")+
  mytheme
```
```{r primary_dept_nums, fig.width=8, fig.height=3.5,fig.align = "center"}
#yearly_primary
ggplot(yearly_primary, aes(year))+
  geom_bar(color ="grey50", fill ="lightblue") +
  xlab("year")+
  ylab("counts")+
  ggtitle("Number of Responsible Departments via years")+
  mytheme
```
As can be seen from the bar charts above, the number of proposals improved rapidly before 2017 and came to a peak in year 2017. After 2017, the number of proposals remained at a high level. Similarly to the number of proposals, the number of participating home departments is also in an increasing trend. However, the increase is relatively slow. Different from proposals and home departments, the number of primary responsible departments doesn't have an obvious upward trend via years. Instead, the number reaches the bottom in 2018.